Trajectories

### 2021-09-15 Rmd/report.Rmd
Add GitHub dark theme

---
title: "Trajectories"
output:
  html_document: default
  github_document:
    pandoc_args: --webtex
bibliography: "trajectories.bib"
---

@@

(by_cognate / by_language) + by_class +
  plot_layout(2) &
  theme_custom() &
  theme(
    legend.position = "none",
    axis.title.y = element_blank(),
    panel.grid.major.y = element_blank()
  )

@@

by_cognate / by_class +
  plot_layout() &
  theme_custom() +
  theme(
    panel.grid.major.y = element_blank(),
    axis.title.y = element_blank(),
    legend.position = "right",
    legend.title = element_blank()
  )

@@

```{r participants_time, message=FALSE, warning=FALSE, paged.print=FALSE}
participants %>% 
  group_by(time_stamp, lp, dominant_language) %>% 
  summarise(n = n(), .groups = "drop") %>% 
  group_by(lp, dominant_language) %>% 
  mutate(n = cumsum(n)) %>% 
  ggplot(aes(time_stamp, n, colour = interaction(lp, dominant_language, sep = " - "), fill = interaction(lp, dominant_language, sep = " - "))) +
  geom_line(size = 1) +
  labs(x = "Date", y = "Number of responses", colour = "LP - Dominant language") +
  scale_y_continuous(breaks = seq(0, 250, 50)) +
  guides(colour = guide_legend(ncol = 2)) +
  theme_custom() +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    axis.title.x = element_blank(),
  )

@@

participants %>% 
  mutate(age = round(age)) %>% 
  count(lp, dominant_language, age) %>% 
  ggplot(aes(as.factor(age), n, fill = interaction(lp, dominant_language, sep = " - "))) +
  geom_col(position = position_fill(), colour = "white") +
  guides(colour = guide_legend(ncol = 2)) +
  coord_flip() +
  labs(y = "Proportion of the sample", x = "Age (months)", colour = "LP - Dominant language") +
  scale_y_continuous(labels = scales::percent) +
  theme_custom() +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
  ) +

  participants %>% 
  mutate(age = round(age)) %>% 
  count(lp, dominant_language, age) %>% 
  ggplot(aes(as.factor(age), n, fill = interaction(lp, dominant_language, sep = " - "))) +
  geom_col(colour = "white") +
  labs(y = "Number of participants", x = "Age (months)") +
  guides(colour = guide_legend(ncol = 2)) +
  theme_custom() +
  coord_flip() +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank()
  ) +

@@

```{r vocabulary_long_comprehension, message=FALSE, warning=FALSE, paged.print=FALSE}
vocabulary$long %>% 
  filter(type=="understands") %>% 
  ggplot(aes(value, reorder(id, age), colour = version, fill = version, shape = version)) +
  facet_grid(~scale) +
  geom_point() +
  labs(x= "Vocabulary size", y = "Participant (ordered by age, min-to-max)",
       colour = "Version", fill = "Version", shape = "Version") +
  scale_x_continuous(labels = scales::percent) +
  theme_bw() +
  theme(
    legend.position = "top",
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )
```

@@

```{r vocabulary_long_production, message=FALSE, warning=FALSE, paged.print=FALSE}
vocabulary$long %>% 
  filter(type=="produces") %>% 
  ggplot(aes(value, reorder(id, age), colour = version, fill = version, shape = version)) +
  facet_grid(~scale) +
  geom_point() +
  labs(x= "Vocabulary size", y = "Participant (ordered by age, min-to-max)",
       colour = "Version", fill = "Version", shape = "Version") +
  scale_x_continuous(labels = scales::percent) +
  theme_bw() +
  theme(
    legend.position = "top",
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )
```

@@

```{r raw, message=FALSE, warning=FALSE, paged.print=FALSE}
responses %>%
  group_by(te, cognate) %>%
  summarise(
    understands = mean(understands, na.rm = TRUE),
    produces = mean(produces, na.rm = TRUE)
  ) %>%
  pivot_longer(
    c(understands, produces),
    names_to = "type",
    values_to = "prop"
  ) %>%
  mutate(type = str_to_sentence(type)) %>% 
  ggplot(aes(prop, reorder(te, -prop), colour = cognate)) +
  facet_wrap(vars(type)) +
  geom_vline(xintercept = 0.5, linetype = "dotted", size = 1) +
  geom_point(alpha = 0.5, size = 2) +
  labs(x = "Mean % of acquisition", y = "Translation equivalent ID", colour = "Type") +
  scale_x_continuous(limits = c(0, 1), labels = scales::percent) +
  theme_custom() +
  theme(
    legend.position = "top",
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
  )
```

```{r raw_age, message=FALSE, warning=FALSE, paged.print=FALSE}
responses %>%
  mutate(age = as.factor(round(age))) %>% 
  group_by(te, age, cognate) %>%
  summarise(
    understands = mean(understands, na.rm = TRUE),
    produces = mean(produces, na.rm = TRUE)
  ) %>%
  pivot_longer(
    c(understands, produces),
    names_to = "type",
    values_to = "prop"
  ) %>%
  mutate(type = str_to_sentence(type)) %>% 
  ggplot(aes(age, prop, colour = cognate, fill = cognate, shape = cognate)) +
  facet_wrap(vars(type)) +
  geom_hline(yintercept = 0.5, linetype = "dotted", size = 1) +
  geom_point(aes(group = interaction(age, cognate)), alpha = 0.5, size = 0.5) +
  stat_summary(fun.data = mean_se, geom = "pointrange") +
  labs(x = "Mean % of acquisition", y = "Translation equivalent ID",
       colour = "Cognate", shape = "Cognate", fill = "Cognate") +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  theme_custom() +
  theme(
    legend.position = "top",
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid = element_blank(),
    legend.title = element_blank()
  )
```

@@

ggplot(post, aes(.value)) +
  facet_wrap(~.variable, scales = "free_x") +
  geom_vline(xintercept = 0, size = 1, colour = "grey") +
  stat_histinterval(fill = "lightblue") +
  labs(x = "Value", y = "Posterior probability density", fill = "Variable") +
  theme_custom() +
  theme(
    legend.position = "none",
    plot.caption.position = "plot",
    plot.caption = element_text(hjust = 0),
    # axis.text = element_text(size = 7),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
  )
```

@@

ggplot(re_id, aes(Estimate, reorder(id, Estimate))) +
  geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), size = 0.25,
                 colour = wes_palettes$Darjeeling1[1]) +
  geom_point(size = 1, shape = "|") +
  geom_vline(xintercept = 0.5, linetype = "dashed") +
  labs(x = "Participant average probability of comprehension",
       y = "Participant") +
  scale_x_continuous(limits = c(0, 1)) +
  theme_custom() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    panel.grid = element_blank()
  )

@@

ggplot(re_te, aes(Estimate, reorder(te, Estimate))) +
  geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), size = 0.25,
                 colour = wes_palettes$Darjeeling1[2]) +
  geom_point(size = 1, shape = "|") +
  geom_vline(xintercept = 0.5, linetype = "dashed") +
  labs(x = "Item average probability of comprehension",
       y = "Item") +
  scale_color_brewer(palette = "Set1") +
  scale_x_continuous(limits = c(0, 1)) +
  theme_custom() +
  theme(
    axis.text.y = element_blank(),
    panel.grid = element_blank(),
    axis.ticks = element_blank()
  )
```

@@

  # stat_lineribbon(size = 0, alpha = 0.5, .width = 0.95) +
  # stat_summary(fun = "mean", geom = "line", size = 1) +
  geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
  labs(x = "Age (months)", y = "P(Comprehension)", colour = "Cognateness", fill = "Cognateness") +
  scale_y_continuous(labels = scales::percent) +
  theme_custom() +
  theme(
    legend.position = "right",
    legend.title = element_blank()
  )

@@

gather_draws(fits$fit_2, `b_.*`, `sd_te__.*`, `cor_te__.*`, regex = TRUE) %>% 
  mutate(.chain = paste("Chain ", .chain)) %>% 
  ggplot(aes(.iteration, .value, colour = .chain)) +
  facet_wrap(~.variable, scales = "free_y") +
  annotate(geom = "rect", colour = NA, xmin = 0, xmax = 500, ymin = -Inf, ymax = Inf, alpha = 0.25, colour = "grey") +
  geom_line(alpha = 0.5) +
  labs(x = "Iteration", y = "Sample value", colour = "Chain") +
  theme_custom() +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    panel.grid = element_blank()
  )

>>>>

---
title: "Trajectories"
output:
  github_document:
    pandoc_args: --webtex
bibliography: "trajectories.bib"
---

@@

(by_cognate / by_language) + by_class +
  plot_layout(2) &
  theme_github() &
  theme(
    legend.position = "none",
    axis.title.y = element_blank(),
    panel.grid.major.y = element_blank()
  )

@@

by_cognate / by_class +
  plot_layout() &
  theme_github() +
  theme(
    panel.grid.major.y = element_blank(),
    axis.title.y = element_blank(),
    legend.position = "right",
    legend.title = element_blank()
  )

@@

```{r participants_time, message=FALSE, warning=FALSE, paged.print=FALSE}
participants %>% 
  group_by(time_stamp, lp, dominant_language) %>% 
  summarise(n = n(), .groups = "drop") %>% 
  group_by(lp, dominant_language) %>% 
  mutate(n = cumsum(n)) %>% 
  ggplot(aes(time_stamp, n, colour = interaction(lp, dominant_language, sep = " - "), fill = interaction(lp, dominant_language, sep = " - "))) +
  geom_line(size = 1) +
  labs(x = "Date", y = "Number of responses", colour = "LP - Dominant language") +
  scale_y_continuous(breaks = seq(0, 250, 50)) +
  guides(colour = guide_legend(ncol = 2)) +
  theme_github() +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    axis.title.x = element_blank(),
  )

@@

participants %>% 
  mutate(age = round(age)) %>% 
  count(lp, dominant_language, age) %>% 
  ggplot(aes(as.factor(age), n, fill = interaction(lp, dominant_language, sep = " - "))) +
  geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
  guides(colour = guide_legend(ncol = 2)) +
  coord_flip() +
  labs(y = "Proportion of the sample", x = "Age (months)", colour = "LP - Dominant language") +
  scale_y_continuous(labels = scales::percent) +
  theme_github() +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
  ) +

  participants %>% 
  mutate(age = round(age)) %>% 
  count(lp, dominant_language, age) %>% 
  ggplot(aes(as.factor(age), n, fill = interaction(lp, dominant_language, sep = " - "))) +
  geom_col(size = 1, colour = "#0D1117") +
  labs(y = "Number of participants", x = "Age (months)") +
  guides(colour = guide_legend(ncol = 2)) +
  theme_github() +
  coord_flip() +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank()
  ) +

@@

```{r vocabulary_long_comprehension, message=FALSE, warning=FALSE, paged.print=FALSE}
vocabulary$long %>% 
  filter(type=="understands") %>% 
  ggplot(aes(value, reorder(id, age), colour = version, fill = version, shape = version)) +
  facet_grid(~scale) +
  geom_point() +
  labs(x= "Vocabulary size", y = "Participant (ordered by age, min-to-max)",
       colour = "Version", fill = "Version", shape = "Version") +
  scale_x_continuous(labels = scales::percent) +
  theme(
    legend.position = "top",
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )
```

@@

```{r vocabulary_long_production, message=FALSE, warning=FALSE, paged.print=FALSE}
vocabulary$long %>% 
  filter(type=="understands") %>% 
  ggplot(aes(value, reorder(id, age), colour = version, fill = version, shape = version)) +
  facet_grid(~scale) +
  geom_point() +
  labs(x= "Vocabulary size", y = "Participant (ordered by age, min-to-max)",
       colour = "Version", fill = "Version", shape = "Version") +
  scale_x_continuous(labels = scales::percent) +
  theme_github() +
  theme(
    panel.grid.major.y = element_blank(),
    legend.position = "top",
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )
```

@@

```{r raw, message=FALSE, warning=FALSE, paged.print=FALSE}
responses %>%
  group_by(te, cognate) %>%
  summarise(
    understands = mean(understands, na.rm = TRUE),
    produces = mean(produces, na.rm = TRUE)
  ) %>%
  pivot_longer(
    c(understands, produces),
    names_to = "type",
    values_to = "prop"
  ) %>%
  mutate(type = str_to_sentence(type)) %>% 
  ggplot(aes(prop, reorder(te, -prop), colour = cognate)) +
  facet_wrap(vars(type)) +
  geom_vline(xintercept = 0.5, linetype = "dotted", size = 1) +
  geom_point(alpha = 0.5, size = 2) +
  labs(x = "Mean % of acquisition", y = "Translation equivalent ID", colour = "Type") +
  scale_x_continuous(limits = c(0, 1), labels = scales::percent) +
  theme_github() +
  theme(
    legend.position = "top",
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
  )
```

```{r raw_age, message=FALSE, warning=FALSE, paged.print=FALSE}
responses %>%
  mutate(age = as.factor(round(age))) %>% 
  group_by(te, age, cognate) %>%
  summarise(
    understands = mean(understands, na.rm = TRUE),
    produces = mean(produces, na.rm = TRUE)
  ) %>%
  pivot_longer(
    c(understands, produces),
    names_to = "type",
    values_to = "prop"
  ) %>%
  mutate(type = str_to_sentence(type)) %>% 
  ggplot(aes(age, prop, colour = cognate, fill = cognate, shape = cognate)) +
  facet_wrap(vars(type)) +
  geom_hline(yintercept = 0.5, linetype = "dotted", size = 1) +
  geom_point(aes(group = interaction(age, cognate)), alpha = 0.5, size = 0.5) +
  stat_summary(fun.data = mean_se, geom = "pointrange") +
  labs(x = "Mean % of acquisition", y = "Translation equivalent ID",
       colour = "Cognate", shape = "Cognate", fill = "Cognate") +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  theme_github() +
  theme(
    legend.position = "top",
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid = element_blank(),
    legend.title = element_blank()
  )
```

@@

ggplot(post, aes(.value)) +
  facet_wrap(~.variable, scales = "free_x") +
  geom_vline(xintercept = 0, size = 1, colour = "grey") +
  stat_histinterval(fill = "lightblue") +
  labs(x = "Value", y = "Posterior probability density", fill = "Variable") +
  theme_github() +
  theme(
    legend.position = "none",
    plot.caption.position = "plot",
    plot.caption = element_text(hjust = 0),
    # axis.text = element_text(size = 7),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
  )
```

@@

ggplot(re_id, aes(Estimate, reorder(id, Estimate))) +
  geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), size = 0.25,
                 colour = wes_palettes$Darjeeling1[1]) +
  geom_point(size = 1, shape = "|") +
  geom_vline(xintercept = 0.5, linetype = "dashed") +
  labs(x = "Participant average probability of comprehension",
       y = "Participant") +
  scale_x_continuous(limits = c(0, 1)) +
  theme_github() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    panel.grid = element_blank()
  )

@@

ggplot(re_te, aes(Estimate, reorder(te, Estimate))) +
  geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), size = 0.25,
                 colour = wes_palettes$Darjeeling1[2]) +
  geom_point(size = 1, shape = "|") +
  geom_vline(xintercept = 0.5, linetype = "dashed") +
  labs(x = "Item average probability of comprehension",
       y = "Item") +
  scale_color_brewer(palette = "Set1") +
  scale_x_continuous(limits = c(0, 1)) +
  theme_github() +
  theme(
    axis.text.y = element_blank(),
    panel.grid = element_blank(),
    axis.ticks = element_blank()
  )
```

@@

  # stat_lineribbon(size = 0, alpha = 0.5, .width = 0.95) +
  # stat_summary(fun = "mean", geom = "line", size = 1) +
  geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
  labs(x = "Age (months)", y = "P(Comprehension)", colour = "Cognateness", fill = "Cognateness") +
  scale_y_continuous(labels = scales::percent) +
  theme_github() +
  theme(
    legend.position = "right",
    legend.title = element_blank()
  )

@@

gather_draws(fits$fit_2, `b_.*`, `sd_te__.*`, `cor_te__.*`, regex = TRUE) %>% 
  mutate(.chain = paste("Chain ", .chain)) %>% 
  ggplot(aes(.iteration, .value, colour = .chain)) +
  facet_wrap(~.variable, scales = "free_y") +
  annotate(geom = "rect", colour = NA, xmin = 0, xmax = 500, ymin = -Inf, ymax = Inf, alpha = 0.25, colour = "grey") +
  geom_line(alpha = 0.5) +
  labs(x = "Iteration", y = "Sample value", colour = "Chain") +
  theme_github() +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    panel.grid = element_blank()
  )
